Staged Abstract Interpreters

### 2018-04-19 paper/paper.tex
update

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review,anonymous]{acmart}
\documentclass[sigplan,anonymous,review]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

In this section, we firstly review their work of closure generation, and reproduce abstractly complied analysis
by adding explicit staging annotation to the CE abstract interpreter.
Show that abstract compilation can be understood as an instance of staged 
abstract interpreter.

@@

@@

@@

@@

Not sure how much improvement of performance.

>>>>

%% For double-blind review submission, w/o CCS and ACM Reference (max submission space)
\documentclass[acmsmall,review,anonymous]{acmart}
%\documentclass[sigplan,anonymous,review]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For double-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review,anonymous]{acmart}\settopmatter{printfolios=true}
%% For single-blind review submission, w/o CCS and ACM Reference (max submission space)
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true,printccs=false,printacmref=false}
%% For single-blind review submission, w/ CCS and ACM Reference
%\documentclass[acmsmall,review]{acmart}\settopmatter{printfolios=true}
%% For final camera-ready submission, w/ required CCS and ACM Reference
%\documentclass[acmsmall]{acmart}\settopmatter{}

@@

In this section, we firstly review their work of closure generation,
and reproduce their result by adding stage annotations to 0-CFA.
Show that \citeauthor{Boucher:1996:ACN:647473.727587}'s abstract compilation can be understood as an instance of staged 
abstract interpreter.

@@

(Specific -> General vs General vs Specific)

@@

\subsection{Abstract Interpreter}

@@

General insights when staging a static analysis algorithm.

Big-step vs small-step

operational vs denotational

\subsection{Adding Stage Annotations}

@@
